Live Functional Programming with Typed Holes

### 2018-02-25 calculus.tex
some layout tweaks and placeholders
fig-syntax
fig-expansion
fig-typing-dexp

@@

\input{fig-type-consistency}

\input{fig-bidirectional-typing}

\input{fig-expansion}

\input{fig-typing-dexp}

\input{fig-substitution}

\input{fig-dynamics-aux}

\input{fig-dynamics-steps}

\input{fig-dynamics-contexts}

@@

%% \begin{figure}[!ht]
  \begin{definition}
    $\hasType{\Delta}{\hGamma}{\sigma}{\hGamma'}$ iff for each $\dexp/x \in \sigma$, we have $x : \htau \in \hGamma'$ and $\hasType{\Delta}{\hGamma}{\dexp}{\htau}$.
  \end{definition}
%%   \caption{substitution type assignment}
%%   \label{fig:subassign}
%% \end{figure}

>>>>

\subsection{Calculus}

\subsubsection{Syntax}

@@

{\color{gray}\blindtext}

Shorthand:

$$
\dcastthree{\dexp}{\htau_1}{\htau_2}{\htau_3} \defeq
  \dcasttwo{\dcasttwo{\dexp}{\htau_1}{\htau_2}}{\htau_2}{\htau_3}
$$

Explain that $c$ is a placeholder constant (i.e., unit), $b$ is a placeholder
type (i.e., unit).

\subsubsection{Statics}

\input{fig-type-consistency}
\input{fig-bidirectional-typing}

{\color{gray}\blindtext}
{\color{gray}\blindtext}
{\color{gray}\blindtext}

A typing context, $\hGamma$, is a list of bindings $x : \htau$.

\subsubsection{Expansion}

\input{fig-expansion}
\input{fig-typing-dexp}

{\color{gray}\blindtext}
{\color{gray}\blindtext}
{\color{gray}\blindtext}

A hole context, $\hDelta$, is a list of bindings $\Dbinding{u}{\hGamma}{\htau}$.

\subsubsection{Dynamics}

\input{fig-substitution}
\input{fig-dynamics-aux}
\input{fig-dynamics-steps}
\input{fig-dynamics-contexts}

{\color{gray}\blindtext}
{\color{gray}\blindtext}
{\color{gray}\blindtext}
{\color{gray}\blindtext}
{\color{gray}\blindtext}

\subsubsection{Examples}

@@

%% \begin{figure}[!ht]
%%   \begin{definition}
%%     $\hasType{\Delta}{\hGamma}{\sigma}{\hGamma'}$ iff for each $\dexp/x \in \sigma$, we have $x : \htau \in \hGamma'$ and $\hasType{\Delta}{\hGamma}{\dexp}{\htau}$.
%%   \end{definition}
%%   \caption{substitution type assignment}
%%   \label{fig:subassign}
%% \end{figure}
